Doubly-Robust Inference in R using \\texttt{drtmle}

### 2022-06-24 paper/preamble.tex
more edits to build

% Any additional packages needed should be included after obs_study_style.
% Note that obs_study_style.sty includes epsfig, amssymb, natbib and graphicx,
% and defines many common macros, such as 'proof' and 'example'.
%
% It also sets the bibliographystyle to plainnat; for more information on
% natbib citation styles, see the natbib documentation, a copy of which

\usepackage[utf8]{inputenc}
\usepackage{mathtools}
\usepackage{amsmath}
\usepackage{fancyvrb}
\usepackage{obs_study_style}

% Definitions of handy macros can go here
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\newcommand{\dataset}{{\cal D}}
\newcommand{\fracpartial}[2]{\frac{\partial #1}{\partial  #2}}
\DefineVerbatimEnvironment{Sinput}{Verbatim}{fontshape=sl}
\DefineVerbatimEnvironment{Soutput}{Verbatim}{}
\DefineVerbatimEnvironment{Scode}{Verbatim}{fontshape=sl}
\newenvironment{Schunk}{}{}
\DefineVerbatimEnvironment{Code}{Verbatim}{}
\DefineVerbatimEnvironment{CodeInput}{Verbatim}{fontshape=sl}
\DefineVerbatimEnvironment{CodeOutput}{Verbatim}{}
\newenvironment{CodeChunk}{}{}
\setkeys{Gin}{width=0.8\textwidth}

@@

\author{
  \name David Benkeser \email benkeser@emory.edu \\
  \addr Department of Biostatistics \& Bioinformatics\\
  Rollins School of Public Health\\
  Emory University\\
  1518 Clifton Road, N.E., Atlanta, GA 30322
  \AND
  \name Nima S.~Hejazi \email nhejazi@hsph.harvard.edu \\
  \addr Department of Biostatistics\\
  T.H.~Chan School of Public Health\\
  Harvard University \\
  677 Huntington Avenue, Boston, MA 02115
}

>>>>

% Any additional packages needed should be included after obs_study_style.
% Note that obs_study_style.sty includes epsfig, amssymb, natbib and graphicx,
% and defines many common macros, such as 'proof' and 'example'.
%
% It also sets the bibliographystyle to plainnat; for more information on
% natbib citation styles, see the natbib documentation, a copy of which
\usepackage{obs_study_style}
\usepackage[utf8]{inputenc}
\usepackage{mathtools}
\usepackage{amsmath}
\usepackage{fancyvrb}
\usepackage[pdfstartview=FitH]{hyperref}
\usepackage{bookmark}

% Definitions of handy macros can go here
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}
}
\newcommand{\dataset}{{\cal D}}
\newcommand{\fracpartial}[2]{\frac{\partial #1}{\partial  #2}}
\DefineVerbatimEnvironment{Sinput}{Verbatim}{fontshape=sl}
\DefineVerbatimEnvironment{Soutput}{Verbatim}{}
\DefineVerbatimEnvironment{Scode}{Verbatim}{fontshape=sl}
\newenvironment{Schunk}{}{}
\DefineVerbatimEnvironment{Code}{Verbatim}{}
\DefineVerbatimEnvironment{CodeInput}{Verbatim}{fontshape=sl}
\DefineVerbatimEnvironment{CodeOutput}{Verbatim}{}
\newenvironment{CodeChunk}{}{}
\setkeys{Gin}{width=0.8\textwidth}

@@

\author{
  \name David Benkeser \email benkeser@emory.edu\\
  \addr Department of Biostatistics \& Bioinformatics\\
  Rollins School of Public Health\\
  Emory University\\
  1518 Clifton Road, N.E.,\\
  Atlanta, GA 30322
  \AND
  \name Nima S.~Hejazi \email nhejazi@hsph.harvard.edu\\
  \addr Department of Biostatistics\\
  T.H.~Chan School of Public Health\\
  Harvard University\\
  677 Huntington Avenue,\\
  Boston, MA 02115
}

### 2022-06-24 paper/using_drtmle_obstudies.Rmd
more edits to build

---
output:
  bookdown::pdf_document2:
    includes:
      in_header: preamble.tex
bibliography: refs.bib
---

@@

As an intermediate step, the AIPTW and TML estimators require estimation of
two key nuisance parameters: the probability of treatment as a function of
confounders (the propensity score, hereafter referred to as the *PS*) and the
average outcome as a function of confounders and treatment (the outcome
regression, *OR*). In addition to their desirable inferential properties, AIPTW
and TML estimators also enjoy a *double robustness* property. That is, the
estimators are consistent for the population-level effect of interest if either
of the PS or OR is consistently estimated. This property gives the AIPTW and
TML estimators a natural appeal: inconsistency in the estimation of one
nuisance parameter may be mitigated by the consistent estimation of the other.
However, recent work has shown that the double robustness property does not
necessarily extend to the inferential properties of these estimators when
adaptive estimators of the PS and/or OR are used
[@vdl:2014:ijb,@benkeser:2017:biometrika]. Instead, valid inference requires
consistent estimation of *both* the PS *and* the OR. @vdl:2014:ijb
proposed new TML estimators that have an asymptotic normal sampling distribution
with estimable variance under consistent estimation of *either* the PS *or* the
OR, paving the way for inference that is doubly-robust.
@benkeser:2017:biometrika proposed modifications of these estimators with
similar robustness properties and illustrated their practical performance.

>>>>

---
output:
  latex_fragment:
    includes:
      in_header: preamble.tex
bibliography: refs.bib
---

@@

As an intermediate step, the AIPTW and TML estimators require estimation of two
key nuisance parameters: the probability of treatment as a function of
confounders (the propensity score, hereafter referred to as the *PS*) and the
average outcome as a function of confounders and treatment (the outcome
regression, *OR*). In addition to their desirable inferential properties, AIPTW
and TML estimators also enjoy a *double robustness* property. That is, the
estimators are consistent for the population-level effect of interest if either
of the PS or OR is consistently estimated. This property gives the AIPTW and TML
estimators a natural appeal: inconsistency in the estimation of one nuisance
parameter may be mitigated by the consistent estimation of the other. However,
recent work has shown that the double robustness property does not necessarily
extend to the inferential properties of these estimators when adaptive
estimators of the PS and/or OR are used
[@vdl:2014:ijb, @benkeser:2017:biometrika]. Instead, valid inference requires
consistent estimation of *both* the PS *and* the OR. @vdl:2014:ijb proposed new
TML estimators that have an asymptotic normal sampling distribution with
estimable variance under consistent estimation of *either* the PS *or* the OR,
paving the way for inference that is doubly-robust. @benkeser:2017:biometrika
proposed modifications of these estimators with similar robustness properties
and illustrated their practical performance.
